---
title: "The R 'afgencomp' Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{afgencomp-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Background & Description 

This document is the package vignette for the `afgencomp' package in R.  The 
code in this package was originally included in a github package distributed 
under the name `YinGenomicDFTDistances'.  This is the most current version of 
the software from the previous package, and all associated works.  

This software is developed independently from many of the extant enhanced 
datatypes which are available within the BioConductor software suite, as it is 
intended to be a light-weight standalone package which can be used to quickly 
produce distances between genomic sequences using alignment free methods.  This 
being said, the primary data-type utilized for storing sequences is the string. 

# Package Installation

This vignette is distributed and maintained along with the software in `afgencomp'. 
However, if you happen to find your way to this vignette, and are looking to install 
the `afgencomp' R-package you may do so via one of several routes: 

* Install the Software from A Source Distribution
* Install the Software from the Github Repository using `devtools::install_github()'
* (Coming Soon) Install the Software from CRAN using `install.packages' 

## Installing The Software from Source 

The source distribution of the software is written in R, and hosted on Github. 
The source code can be downloaded using the git software to clone the afgencomp 
repository
```{r setup}
library(afgencomp)
```
